A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-07-24 review/response.letter.tex

\title{Reply to Reviewer's Comments on\\
``A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation''}
\author{}

\begin{document}

\maketitle
\pagenumbering{roman}
\setcounter{page}{1}

We are grateful to all the reviewer for  the time taken to pointing out relevant issues in our manuscript.

@@

Detailed minor comments:

\begin{itemize}
\item - The abstract and introduction (specifically) suffer from English/grammar issues. (e.g. "eskeletomuscular" to musculoskeletal); the reviewer recommends the paper be peer-edited by a native speaker if it has not been already.
\item - The footer says the paper has been "revised August 26, 2020", which is of course a date that has not happened yet.
\item - The term $Dt{off}$ is often spelled $Dt{o}ff$ and should be fixed (same with $Dm{off}$).
\item - The caption for Table 1 should be with the actual table, not in a separate column.
\item - In Figure 5 it is not visible that a marker is placed on the side of the robot, nor on the hand of the patient (also the patient is not wearing a glove which is mentioned in the paper).
\end{itemize}

Page 6, first paragraph: "a high cr was important so the robot can turn quickly to point to the leader, but high values of cr should be avoided"; this seems contradictory.

\section*{\fbox{Associate Editor Responses:}}

\begin{quotation}
{\color{blue}
We appreciate for the Associate Editor's comments.  We concentrated our efforts modifying the manuscript in the two important lines that the Editor recommended.

We addressed the first issue by adding a new Section "Comparison with alternative methods" where we compared the tethered controller with one and two threads and compared our proposal with other alternative proposals from the literature.  We also included an evaluation of technical aspects of the design.

Regarding the second issue, we performed an additional experiment on the simulation environment where we included a 5 kg mass, in a 45 degrees orientation, according to the weight and size of the oxygen tank regularly used at ALPI.  We verified in the simulation that we obtained results very similar to the those obtained without the tank and that the controlling algorithm worked within the safe boundaries that we defined and that the following behavior was satisfied.
}
\end{quotation}

@@

%\subsection*{\ovalbox{Reviewer 1 General Comments}}

I found the work interesting and tackling an important problem, which can have applications outside support in this specific task. The need to carry oxygen tanks around patients with respiratory problems is high in hospitals and rehabilitation facilities. This solution frees nurses or other medical staff that would be occupied with such tasks and even patients that could carry the tank themselves with such solution can have an easier life in these places.

Overall the article is very well written, I've found some typos to which I'll refer in a momment. The idea is transmitted clearly and the authors did an excellent job motivating the problem and covering the relevant literature. The prototype defined solves the problem in an elegant and simple way and I find the documentation on how the robot was designed sufficient. However, Section II.D, the control strategy section, could have explored more the strategies as some variables and expressions are not entirely clear regarding their aim; despite that the reader can understand how each strategy works and their differences.

\begin{quotation}
{\color{blue}
We thanks very much, the Reviewer, for the positive appraisal.  We revised the notation on Section II.D.  We also added a section to establish the parallels between a single and double thread configuration, comparing the solution to other alternatives found in the literature.  We clarified all the variables and their physical meaning and included an extra Figure to aid in the provided explanation.
}
\end{quotation}

@@

Regarding the evaluation and discussion I don't have much to add, I believe you conducted two solid validations of the system that showed the system performs adequately and the conclusions from those studies seem in line with both the results and the clinical assessment performed. My only question is why were the configurations used in the real world study not part of the set of configurations used in the simulation? I understand why you reduced the sets of configurations used in the real world study, but I would expect that those sets would come from the simulations ran not entirely new sets of configurations. I think this part should have been better explained.

\begin{quotation}
{\color{blue}
During the simulation we explored different sets of values for the controller parameters.  Once we arrived to parameter values where we obtain a range of satisfactory results in terms of the metrics that we defined, we moved forward to the real world testing of the prototype.  We found that we had to fine-tune the parameters to adapt them to the real world scenario.  However, the relative relation between parameters was consistent on both the simulation and in the real world, and that helped us to avoid searching extensively the parameter space for the real world scenario.  We added in the manuscript a clarification of this point in Section VI.
}
\end{quotation}

@@

Overall, the reviewer found the application to be interesting; it seems like a great opportunity for a robotic solution. The experiments conducted appear to be reasonably selected. It is unclear, however, what the significance of the work is, particularly in the context of previous work [1] which also investigates a tethered robot solution for COPD rehabilitation. The discernible differences between the proposed work and that within [1] appear to be that the proposed robot has two tethers instead of one, and that the solution can be used in medical facilities instead of home therapy environments (the latter of which would probably have even more complicated navigation environments). There is no comparison between this existing work and the proposed work which, given they are essentially tackling the same application, is problematic: what are the advantages/disadvantages of one design over another? Is there something specifically wrong with the design in [1] that prompted the authors to develop their own approach?

\vspace{2em}

[1]  Endo, Gen, et al. "Mobile follower robot as an assistive device for home oxygen therapy–evaluation of tether control algorithms." ROBOMECH Journal 2.1 (2015): 1-9.

\begin{quotation}
{\color{blue}
We added a new specific section to address this issue.  Now in Section III "Comparison with alternative methods", we show that the proposed algorithm based on two threads is equivalent to the one presented in the work [1].  We added a new Figure 5 to aid in the explanation.  Additionally, we included an additional "Design Analysis" section comparing both alternatives (two threads, and one thread and an angle).  Moreover, we modified the notation to allow an improved comparison with previous proposals.
}
\end{quotation}

@@

There were also a number of technical elements the reviewer had a hard time understanding:
- How are "pulses" defined (equation (1)), and how is this value used in an equation?

\begin{quotation}
{\color{blue}
We refer to pulses as a discrete number obtained directly from the rotary encoder KY-040.  The encoder generates two digital pulses, one that indicates the presence of movement and the other is the direction of movement.  This digital encoder is connected to the microcontroller and it generates an interruption each time the encoder produces a rotational movement.  By reading the additional pulse, the direction can be determined and the value for pulses represents the relative circular distance traveled by the reel wheel.   We added the definition of pulses in the manuscript on Section II.A.
}
\end{quotation}

@@

- How does a distance multiplied by a constant yield a velocity? (equation (2)); It would seem there is some element of time missing here.

\begin{quotation}
{\color{blue}
We appreciate a lot this important issue that the Reviewer is pointing out here.  We modified the notation trying to make it more consistent across the paper and more consistent with previous works as well.  We clarify the units in the proportional gain $c_v$ and $c_{\alpha}$ to make equations physically meaningful.
}
\end{quotation}

@@

- How does a velocity, plus a distance multiplied by a constant yield a power value? (equations (3) and (4)); additionally, using "v" to denote both velocity and power seems like a poor notation choice

\begin{quotation}
{\color{blue}
We added proper units for the constants and modify the equations clarifying that left-hand values reference speeds for each wheel.
}
\end{quotation}

@@

In addition to these comments, it would seem that a robot being designed to carry a heavy oxygen tank would be designed with said tank in mind. The current calibration of constants and experimental results are not done with the weight of a heavy oxygen tank, and thus it is hard to determine if the design and control techniques would actually succeed in their intended application. Is there a reason that a weight of some kind was not used for the experiments? Can non-weighted experiments be justified somehow?

\begin{quotation}
{\color{blue}
We performed an additional simulation and added the obtained results in Section VII.B, at the end of the manuscript.  We modified our simulated prototype and added a $5$ kg oxygen tank at an inclination of 45 degrees, and confirmed that the oxygen supply is not affected by this inclination, and that is under safe usage guidelines for the tank.  The proposed algorithm \textit{Follow the thread} worked in a very similar way as shown in Figure 7, and only constant coefficients had to be readjusted for this purpose.  Results show that the behavior of the robot is similar.  This is a very important feasibility test that allows and encourage us to modify the hardware prototype to include the tank holder, and to move forward to this project's next step.
}
\end{quotation}

@@

Given the issues of significance w.r.t. existing work and technical questions raised, the reviewer recommends major revisions.

Detailed minor comments:

- The abstract and introduction (specifically) suffer from English/grammar issues. (e.g. "eskeletomuscular" to musculoskeletal); the reviewer recommends the paper be peer-edited by a native speaker if it has not been already.

\begin{quotation}
{\color{blue}
We replaced the term with musculoskeletal and verified the English grammar on the Abstract and Introduction section. 
}
\end{quotation}

@@

- The footer says the paper has been "revised August 26, 2020", which is of course a date that has not happened yet.

\begin{quotation}
{\color{blue}
We are very surprised the the fast review process!   We truly thank all the Reviewers for their valuable time.  Dates have now been fixed.
}
\end{quotation}

@@

- The term $Dt{off}$ is often spelled $Dt{o}ff$ and should be fixed (same with $Dm{off}$).

\begin{quotation}
{\color{blue}
We reviewed all the constants definitions and naming conventions to be consistent along the manuscript.
}
\end{quotation}

@@

- The caption for Table 1 should be with the actual table, not in a separate column.

\begin{quotation}
{\color{blue}
This is an issue with Latex reformatting.  We fixed it by modifying the layout of the manuscript.
}
\end{quotation}

- In Figure 5 it is not visible that a marker is placed on the side of the robot, nor on the hand of the patient (also the patient is not wearing a glove which is mentioned in the paper).

\begin{quotation}
{\color{blue}
There are two markers on top of the robot, just above each reel.  They are quite small and the picture lighting does not help.  We modified the Figure caption clarifying all this information.
}
\end{quotation}

Page 6, first paragraph: "a high $c_r$ was important so the robot can turn quickly to point to the leader, but high values of $c_r$ should be avoided"; this seems contradictory.

\begin{quotation}
{\color{blue}
We change the phrase to emphasize that the value of $c_r$ was related with the dynamical behavior of the robot.  We appreciate the Reviewers comment.
}
\end{quotation}

### 2020-07-24 alpibot.tex
Version ready for submission.

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) undergo a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  During Pulmonary Rehabilitation patients perform different exercises and walking activities and may require oxygen assistance.  The oxygen tank cannot be carried by the patient due to the musculoskeletal atrophy that characterize this pathology and external assistance is required.   The assistance to transport the bulky oxygen tank can be provided by a robotic device that follows the patient while performing the physical activities. This work provides an initial study on the controlling mechanism of a differential tethered robot that implements a leader-follower configuration to carry the oxygen tank for these procedures.  Two alternative control strategies are proposed.  Results are simulated and tested on a real prototype in a Motion Capture System.
\end{abstract}

@@

Hence, this work provides an initial study on the controlling mechanism of a differential tethered robot that implements the leader-follower configuration on a Pulmonary Rehabilitation procedure.  To do so, this document unrolls as follows.  Section~\ref{materials} poses the problem and the solution design. Section~\ref{experimental} documents the experimental protocol to perform the solution assessment on a simulation and on a real world scenario.  Results and discussions are described in Sections ~\ref{results} and~\ref{discussion}. The clinical assessment performed jointly with medical personnel is tackled in Section~\ref{clinical}.  Finally, conclusions are exposed in the remaining Section~\ref{conclusion}.

@@

\noindent where pulses obtained for each reel encoder are $pulses_{l}$ and $pulses_{r}$ for the left and right encoder. These equations provide the estimated values for the left $l_L$ and right $l_R$  thread distance. The variable $r$ is the radius of the reel and $ppr$ is the pulses per revolution (resolution) of the encoder.  The initial position of the threads is configurable.

@@

The SBC connects to a WiFi network and can receive remote commands to control the robot. It also broadcasts telemetry data to any listening devices on the network. The control algorithms run in this board, which continuously communicates with the Arduino board to receive sensor data and to issue commands to move the motors or retract the reels.   The algorithms are programmed in python 3.7, which allows the exact same code to run both the simulated and real world prototype.

@@

The two reels are designed from PVC extrusions and are shown on Figure~\ref{fig:alpibot2}.  They are attached to regular FA-12350 DC motors scavenged from old compact discs.  Each reel is axially locked to inexpensive Ky-040 rotary encoder which provides around 20 pulses per revolution.
%Hardware specifications are described on table \ref{tab:specifications}.

@@

Two simple algorithmic control strategies are proposed and evaluated.  The first one is called Follow-the-thread and the second strategy is Rotate and go.  %The Adafruit Shield controller provides a very stable output signal, provided battery are kept above reference.  Hence, wheels motor control is open-loop.

@@

\section{Comparision with alternative methods} \label{development}

@@

\begin{equation}
\begin{array}{ll}  
l_R &= \sqrt[2]{y^2 + {x'}^2} \\
l_L &= \sqrt[2]{y^2 + {x''}^2}. \\
\end{array}
\label{eq:threadsincoordinates}
\end{equation}

From Figure~\ref{fig:dibujitos} we can see that ${x''} + x' =  b$, with $b$ the axle length. Combining this with~\ref{eq:threadsincoordinates}, we can form a system of equations to determine $x'$, $x''$ and $y$:

@@

From the first equation (a), rearranging and squaring both terms leads to

@@

By substracting (b) and (c), it can be obtained

@@

From this equation $x''$ can be determined as

@@

In the scheme proposed by~\cite{Endo2015} a single thread is recovered mechanically by means of a circular flat spring. This device works intensively when the robot is following the patient and, therefore, the spring is exposed to wear. Instead, the double thread recovery implemented by an active reel spring allows a more controlled situation and depends exclusively on the software that controls the reel motor, which can be regulated.

Additionally with a circular flat spring, the spring tension depends on the released thread length, hence the recovery force will vary accordingly. The scheme based on an actuated reel allows a more controlled situation and depends exclusively on the software that controls the reel motor, which can be regulated.

Regarding the control algorithm, authors in \cite{Endo2015} introduced two methods. The first of them computes the angular velocity as a  function of the difference between the measured thread length $l_m$ and the desired distance to patient  $l_D$. In this way, if the patient moves around the robot with a $l_m$ equals to $l_d$, the robot will not adjust its direction until the patient stops turning and continues moving forward. Hence, the robot must correct its direction but the correction angle could be large, which leads the robot to deviate off the desired trajectory. Additionally, the second method proposed is based on dead-reckoning to estimate the patient position. This strategy requires very precise measurements to reduce the cumulative error, which is characteristic of this estimation method~\cite{DurrantWhyte1994}.

@@

\noindent where $ \phi $ is the free parameter, $a$ are the limit length of the arc of the curve, and $x$ and $y$ are the parametric functions that determine the shape of the trajectory on the navigation plane.

@@

The simulation is also useful to study the effects of the different constants in each strategy on the movement of the robot.  The leader starts at the midpoint of the trajectory and completes a full complete circuit getting back to the initial position, while the robot follows its track.  Four different configuration sets of $c_v$ and  $c_{\alpha}$ were tested for Follow the thread, while 6 different configurations were tested for Rotate and go.

@@

A real world experiment was performed, pegging to the same conditions implemented on the simulation environment.  A motion capture system is used to track the movement of a human leader along a predetermined trajectory.   The motion tracking system consists of an array of 16 OptiTrack (NaturalPoint Inc, Oregon, US) Flex 3 cameras, which measure the position of reflective markers with an accuracy of $\pm1$ [cm] at sampling rate of 100 Hz. The calibration and data collection was made using the Motive motion capture software.

As shown on Figure~\ref{fig:capturesystem}, a tracking marker was placed on each side of the robot (on top of each thread reel). The human leader used his hand to grab the tip at which the two tethers were tied together. A third marker was placed in his hand, using a glove. The lemniscate of Gerono, used in the simulation, was marked on the floor, and the human leader tried to move his hand following this shape as close as possible, with stable speed.  The shape was marked according to the shape described in Equation~\ref{eq:lemniscata}, using $a = 2$ [m].

@@

\begin{figure}[h!]
\centering
\includegraphics[width=8cm]{images/capture.png}
\caption{Hardware prototype on the motion capture system and a testing subject holding the threads.  The lemniscate of Gerono was marked on the floor.  The subject follows this track on the performed experiments.}
\label{fig:capturesystem}
\end{figure}

@@

Simulation results for both control strategies are shown on Figure~\ref{fig:simulationresults}. Subfigures (a) and (b) expound the trajectories of the leader and the follower for each strategy, while (c) and (d) describe their speed profiles.  Subfigure (e) show the distance between the robot and the patient for both strategies.  Results metrics for the simulations are shown on Table~\ref{tab:simulationmetricsftt} for the Follow the thread strategy, whereas metrics for Rotate and go are shown on Table~\ref{tab:simulationmetricsrg}.

\begin{center}
\begin{tabular}{ |c|c|c|c| }
\hline
$c_v$ & $c_{\alpha}$ & m.t.d. & t.t.d. \\
\hline
10  &   15  & 0.3614 & 2.0651\\
15  &   5  & 0.4325 & 2.055\\
\textbf{15}  &   \textbf{10}  & \textbf{0.2188} & \textbf{1.0902}\\
15  &   15  & 0.2891 & 1.5059\\
5  &   20  & 0.5733 & 3.7289\\
\hline
\end{tabular}
\captionof{table}{Maximum trajectory deviation m.t.d. [m] and Total trajectory deviation t.t.d. for different Follow the thread constants.}
\label{tab:simulationmetricsftt}
\end{center}

\begin{center}
\begin{tabular}{ |c|c|c|c|c| }
\hline
$c_v$ & $c_r$ & $Dt_{off}$ & m.t.d. & t.t.d.\\
\hline
10  &   20  &   0.1  & 0.4310 & 1.6380\\
20  &   20  &   0.05  & 0.7775 & 3.1139\\
\textbf{20}  &  \textbf{20}  & \textbf{0.1} & \textbf{0.4123} & \textbf{0.9872}\\
20  &   35  &   0.1  & 0.4143 & 1.4820\\
20  &   5  &  0.05  & 0.7815 & 3.0892\\
35  &   20  &   0.1  & 0.6337 & 1.6190\\
\hline
\end{tabular}
\captionof{table}{Maximum trajectory deviation m.t.d. (in [m]) and total trajectory deviation t.p.d. for different Rotate and go constants.}
\label{tab:simulationmetricsrg}
\end{center}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft_a2_n1500_cv15_cr15.eps}
%\caption{Trajectories of the leader and follower for the Follow the thread control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rgv_cv20_cr20_dr10.eps}
%\caption{Trajectories of the leader and follower for Rotate and go control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft_cv15_cr10_leader_robot_speed.eps}
%\caption{Speed profiles of the leader and follower for Follow the thread control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rg_cv20_cr20_bv10_dtoff10_leader_robot_speed.eps}
%\caption{Speed profiles of the leader and follower for Rotate and go control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft_vs_rg_dist.eps}
%\caption{Separation distance between robot and leader for both strategies [m].}
%\label{fig:distance_sim}
%\end{figure}

\begin{figure} 
    \centering
  \subfloat[ \label{sr1a}]{%
       \includegraphics[width=0.49\linewidth]{images/simulation_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{sr1b}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_rotate-go.eps}}
    \\
    \vspace*{-1.1em}
  \subfloat[ \label{sr1c}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{sr1d}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_rotate-go.eps}}
    \\
    \vspace*{-2.5em}
  \subfloat[ \label{sr1e}]{%
        \includegraphics[width=0.99\linewidth]{images/ft_vs_rg_dist.eps}}
  \caption{Simulation Results: Trajectories of the leader and follower for Follow the thread (a) and Rotate and go (b) . 
        Speed profiles of the leader and follower for Follow the thread (c) and Rotate and go (d). 
        (e) Separation distance between robot and leader for both strategies  $[m]$.}
  \label{fig:simulationresults} 
\end{figure}

Results for the real world experiment can be seen on Figure~\ref{fig:realworldresults}.   Table~\ref{tab:cap_ft_npd_table} show the metrics of the Follow the thread strategy, whereas Table~\ref{tab:cap_rg_npd_table} provides the metrics for the Rotate and go approach.

%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft1cap.eps}
%\caption{Trajectories for the Follow the thread control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rg2cap.eps}
%\caption{Distance between robot and leader [m]}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft1cap_leader_robot_speed.eps}
%\caption{Follow the thread speed profiles}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rg2cap_leader_robot_speed.eps}
%\caption{Rotate and go speed profiles}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/cap_ft_vs_rg_dist.eps}
%\caption{Rotate and go speed profiles}
%\label{fig:distance_sim}
%\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) undergo a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  Pulmonary Rehabilitation consists of different physical exercises and walking activities performed at medical facilities under supervision of a physical therapist.  In order to perform these procedures, patients require oxygen assistance, but the oxygen tank cannot be carried by the patient due to the musculoskeletal atrophy that characterize this pathology and external assistance is required.   The assistance to transport the bulky oxygen tank can be provided by a robotic device that follows the patient while performing the physical activities. This work provides an initial study on the controlling mechanism of a differential tethered robot that implements a leader-follower configuration to carry the oxygen tank for these procedures.  Two alternative control strategies are proposed.  Results on a simulated and on a real prototype confirms the feasibility of the proposed solution.
\end{abstract}

%Results on a simulated and on a real prototype, and external validation from professional healthcare givers, confirm the feasibility of the proposed solution.
%While performing Pulmonary Rehabilitation patients perform different exercises and walking activities and may require oxygen assistance.

%Pulmonary Rehabilitation procedures consist of controlled waking activities and physical exercises that patients perform under the supervision of a physical therapist.

@@

Hence, this work provides an initial study on the controlling mechanism of a differential tethered robot that implements the leader-follower configuration on a Pulmonary Rehabilitation procedure.  To do so, this document unrolls as follows.  Section~\ref{materials} and~\ref{Comparison} poses the problem and the solution design. Section~\ref{experimental} documents the experimental protocol to perform the solution assessment on a simulation and on a real world scenario.  Results and discussions are described in Sections ~\ref{results} and~\ref{discussion}. The clinical assessment performed jointly with medical personnel is tackled in Section~\ref{clinical}.  Finally, conclusions are exposed in the remaining Section~\ref{conclusion}.

@@

\noindent where $pulses_{l}$ and $pulses_{r}$ are the pulses obtained for the left and right encoder.  Pulses refer to natural discrete numbers that represents the circular movement of the encoder shaft.  The variable $r$ is the radius of the reel and $ppr$ is the pulses per revolution (resolution) of the encoder. These equations provide the estimated values for the left $l_L$ and right $l_R$  thread distance.   The initial position of the threads is configurable.

@@

The SBC connects to a WiFi network and can receive remote commands to control the robot. It also broadcasts telemetry data to any listening devices on the network. The control algorithms run in this board, which continuously communicates with the Arduino board to receive sensor data and to issue commands to move the motors or retract the reels.   The algorithms are programmed in Python 3.7, which allows the exact same code to run both the simulated and real world prototype.

@@

The two reels are designed from PVC extrusions and are shown on Figure~\ref{fig:alpibot2}.  They are attached to regular FA-12350 DC motors scavenged from old compact discs.  Each reel is axially locked to inexpensive Ky-040 rotary encoder~\cite{SugaharaJunOnoKoji1998} which provides around 20 pulses per revolution.
%Hardware specifications are described on table \ref{tab:specifications}.

@@

Two simple algorithmic control strategies are proposed and evaluated.  The first one is called \textit{Follow the thread} and the second strategy is \textit{Rotate and go}.  %The Adafruit Shield controller provides a very stable output signal, provided battery are kept above reference.  Hence, wheels motor control is open-loop.

@@

\section{Comparison with alternative methods} \label{Comparison}

@@

\begin{equation}
\begin{array}{ll}  
l_R &= \sqrt[2]{y^2 + {x'}^2} \\
l_L &= \sqrt[2]{y^2 + {x''}^2} \\
\end{array}
\label{eq:threadsincoordinates}
\end{equation}

\noindent where $x'$ and $x''$ are the distances from the leader horizontal position to the right and left wheel respectively.

From Figure~\ref{fig:dibujitos} we can see that ${x''} + x' =  b$, with $b$ the axle length. Combining this with Equation~\ref{eq:threadsincoordinates}, we can form a system of equations to determine $x'$, $x''$ and $y$:

@@

From the first Equation (a), rearranging and squaring both terms leads to

@@

By subtracting (b) and (c), it can be obtained

@@

From this equation, $x''$ can be determined as

@@

In the scheme proposed by~\cite{Endo2015} a single thread is recovered mechanically by means of a circular flat spring. This device works intensively when the robot is following the patient and, therefore, the spring is exposed to wear. Additionally with a circular flat spring, the spring tension depends on the released thread length, hence the recovery force will vary accordingly. Instead, the double thread tethered design implemented with an active reel spring allows a more controlled situation and depends exclusively on the software that controls the reel motor, which can be regulated.

Regarding the control algorithm, authors in \cite{Endo2015} introduced two methods. The first of them computes the angular velocity as a  function of the difference between the measured thread length $l_m$ and the desired distance to patient  $l_D$. In this way, if the patient moves around the robot with a $l_m$ equals to $l_D$, the robot will not adjust its direction until the patient stops turning and restarts moving forward. Hence, the robot must correct its direction but the correction angle could be large, which leads the robot to deviate off the desired trajectory. Additionally, the second method proposed is based on dead-reckoning to estimate the patient position. This strategy requires very precise measurements to reduce the cumulative error, which is characteristic of this estimation procedure~\cite{DurrantWhyte1994}.

@@

\noindent where $ \phi $ is the free parameter, $a$ is the limit length of the arc of the curve, and $x$ and $y$ are the parametric functions that determine the shape of the trajectory on the navigation plane.

@@

The simulation is also useful to study the effects of the different constants on the robot movement  for the different strategies.  The leader starts at the midpoint of the trajectory and completes a full circuit getting back to the initial position, while the robot follows its track.  Four different configuration sets of $c_v$ and  $c_{\alpha}$ were tested for \textit{Follow the thread}, while 6 different configurations were tested for \textit{Rotate and go}.

@@

A real world experiment was performed, pegging to the same conditions implemented on the simulation environment.  A motion capture system is used to track the movement of a human leader along a predetermined trajectory.   The motion tracking system consists of an array of 16 OptiTrack (NaturalPoint Inc, Oregon, US) Flex 3 cameras, which measure the position of reflective markers with an accuracy of $\pm1$ cm at sampling rate of 100 Hz. The calibration and data collection was made using the Motive motion capture software.

As shown on Figure~\ref{fig:capturesystem}, a tracking marker was placed on each side of the robot (on top of each thread reel). The human leader used his hand to grab the tip at which the two tethers were tied together. A third marker was placed in his hand, using a glove. The lemniscate of Gerono, used in the simulation, was marked on the floor, and the human leader tried to move his hand following this shape as close as possible, with stable speed.  The shape was marked according to the shape described in Equation~\ref{eq:lemniscata}, using $a = 2$ m.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=8cm]{images/capture.png}
\caption{Hardware prototype on the motion capture system and a testing subject holding the threads.  On top of the device, two markers are placed and an additional marker is on a glove that the user is wearing (not shown on the picture).  The lemniscate of Gerono was marked on the floor.  The subject follows this track on the performed experiments.}
\label{fig:capturesystem}
\end{figure}

@@

Simulation results for both control strategies are shown on Figure~\ref{fig:simulationresults}. Subfigures (a) and (b) expound the trajectories of the leader and the follower for each strategy, while (c) and (d) describe their speed profiles.  Subfigure (e) show the distance between the robot and the patient for both strategies.  Results metrics for the simulations are shown on Table~\ref{tab:simulationmetricsftt} for the \textit{Follow the thread} strategy, whereas metrics for \textit{Rotate and go} are shown on Table~\ref{tab:simulationmetricsrg}.

\begin{center}
\begin{tabular}{ |c|c|c|c| }
\hline
$c_v$ & $c_{\alpha}$ & m.t.d. & t.t.d. \\
\hline
10  &   15  & 0.3614 & 2.0651\\
15  &   5  & 0.4325 & 2.055\\
\textbf{15}  &   \textbf{10}  & \textbf{0.2188} & \textbf{1.0902}\\
15  &   15  & 0.2891 & 1.5059\\
5  &   20  & 0.5733 & 3.7289\\
\hline
\end{tabular}
\captionof{table}{Maximum trajectory deviation m.t.d. (m) and Total trajectory deviation t.t.d. for different \textit{Follow the thread} constants.}
\label{tab:simulationmetricsftt}
\end{center}

\begin{center}
\begin{tabular}{ |c|c|c|c|c| }
\hline
$c_v$ & $c_r$ & $Dt_{off}$ & m.t.d. & t.t.d.\\
\hline
10  &   20  &   0.1  & 0.4310 & 1.6380\\
20  &   20  &   0.05  & 0.7775 & 3.1139\\
\textbf{20}  &  \textbf{20}  & \textbf{0.1} & \textbf{0.4123} & \textbf{0.9872}\\
20  &   35  &   0.1  & 0.4143 & 1.4820\\
20  &   5  &  0.05  & 0.7815 & 3.0892\\
35  &   20  &   0.1  & 0.6337 & 1.6190\\
\hline
\end{tabular}
\captionof{table}{Maximum trajectory deviation m.t.d. (m) and total trajectory deviation t.t.d. for different \textit{Rotate and go} constants.}
\label{tab:simulationmetricsrg}
\end{center}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft_a2_n1500_cv15_cr15.eps}
%\caption{Trajectories of the leader and follower for the \textit{Follow the thread} control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rgv_cv20_cr20_dr10.eps}
%\caption{Trajectories of the leader and follower for \textit{Rotate and go} control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft_cv15_cr10_leader_robot_speed.eps}
%\caption{Speed profiles of the leader and follower for \textit{Follow the thread} control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rg_cv20_cr20_bv10_dtoff10_leader_robot_speed.eps}
%\caption{Speed profiles of the leader and follower for \textit{Rotate and go} control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft_vs_rg_dist.eps}
%\caption{Separation distance between robot and leader for both strategies [m].}
%\label{fig:distance_sim}
%\end{figure}

\begin{figure} 
    \centering
  \subfloat[ \label{sr1a}]{%
       \includegraphics[width=0.49\linewidth]{images/simulation_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{sr1b}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_rotate-go.eps}}
    \\
    \vspace*{-1.1em}
  \subfloat[ \label{sr1c}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{sr1d}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_rotate-go.eps}}
    \\
    \vspace*{-2.5em}
  \subfloat[ \label{sr1e}]{%
        \includegraphics[width=0.99\linewidth]{images/ft_vs_rg_dist.eps}}
  \caption{Simulation Results: Trajectories of the leader and follower for \textit{Follow the thread} (a) and \textit{Rotate and go} (b) . 
        Speed profiles of the leader and follower for \textit{Follow the thread} (c) and \textit{Rotate and go} (d). 
        (e) Separation distance between robot and leader for both strategies  (m).}
  \label{fig:simulationresults} 
\end{figure}

Results for the real world experiment can be seen on Figure~\ref{fig:realworldresults}.   Table~\ref{tab:cap_ft_npd_table} shows the metrics of the \textit{Follow the thread} strategy, whereas Table~\ref{tab:cap_rg_npd_table} provides the metrics for the \textit{Rotate and go} approach.

%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft1cap.eps}
%\caption{Trajectories for the \textit{Follow the thread} control strategy.}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rg2cap.eps}
%\caption{Distance between robot and leader [m]}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/ft1cap_leader_robot_speed.eps}
%\caption{\textit{Follow the thread} speed profiles}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/rg2cap_leader_robot_speed.eps}
%\caption{Rotate and go speed profiles}
%\label{fig:distance_sim}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/cap_ft_vs_rg_dist.eps}
%\caption{\textit{Rotate and go} speed profiles}
%\label{fig:distance_sim}
%\end{figure}
